Scalar_M1

### 2015-05-15 models/Model_Playspace.Rmd
practice commit branch
tinkering with data pipeline - need to fix equally-sized data frames error

```{r}
rm(list=ls())
#p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(rjson)
```

@@

```{r}
priors = read.csv("models/prior.csv")
speaker = read.csv("models/speaker.csv")
listener = read.csv("models/listener.csv")
# none.prob = c(1, 0, 0, 0, 0)
# some.prob = c(.16, .36, .68, .83, .83)
# all.prob = c(.01, .11, .35, .68, .98)

@@

#speaker likelihood helper 
speaker.lhd = function(utt, info, alpha) {
  exp(alpha*(log(info) - 3)) #Rething cost??? 
}

#speaker likelihood normalized
speaker.prob = function(utt, rating, s.matrix, alpha, scale) {
  num = speaker.lhd(utt, s.matrix[rating, utt], alpha)
  norm = 0
  for (i in 1:length(scale) ) {
    current.u = scale[i] #current utterance
    norm = norm + speaker.lhd(current.u, s.matrix[rating, current.u], alpha)
  }
  return(num / norm)
}

#non-normalized posterior
nn.post = function(utt, rating, s.matrix, priors, alpha, scale) {
  return(speaker.prob(utt, rating, s.matrix, alpha, scale) * priors[rating])
}

#normalized posterior
norm.post = function(utt, rating, s.matrix, priors, 
                     alpha = 1, scale = c("low","hi")) {
  nn = nn.post(utt, rating, s.matrix, priors, alpha, scale)
  norm = 0
  for (i in 1:5) {
    norm = norm + nn.post(utt, i, s.matrix, priors, alpha, scale)
  }
  return(nn / norm)
}

@@

```{r}
run.rsa <- function(d) {

  scale.matrix <- d %>% 
    select(stars, degree, speaker.p, prior.p) %>% 
    spread(degree, speaker.p) %>% 
    mutate(hi = hi / sum(hi), 
           low = low / sum(low)) %>%
    as.matrix

  preds <- expand.grid(stars = 1:5, 
              degree = c("low","hi")) %>%
    rowwise %>%
    mutate(listener.pred =  norm.post(scale, stars, 
                                      s.matrix = scale.matrix[,c("low","hi")], 
                                      prior = scale.matrix[,"prior.p"]))

  return(preds)
} 
```

>>>>

```{r}
rm(list=ls())
source("analysis/useful_dplyr.R")
library(rjson)
```

@@

```{r}
priors = read.csv("models/prior.csv")
speaker = read.csv("models/speaker.csv")
listener = read.csv("models/listener.csv")
```

@@

#speaker likelihood helper 
#speaker.lhd = function(utt, info, alpha) {
#  exp(alpha*(log(info) - 3)) #Rething cost??? 
#}
speaker.lhd = function(d) {
  exp(4*(log(d) - 3)) #Rethink alpha and costs?
}

#speaker likelihood normalized
speaker.prob = function(rating, degree, m) {
  num = speaker.lhd(m[rating, degree])
  norm = 0
  for ( i in 1:2 ) {
    norm = norm + speaker.lhd(m[rating, i])
  }
  return(num / norm)
}

#non-normalized posterior
nn.post = function(rating, degree, m) {
  return(speaker.prob(rating, degree, m) * priors[rating, "prior.p"])
}

#normalized posterior
norm.post = function(rating, degree, m) {
  nn = nn.post(rating, degree, m)
  norm = 0
  for (i in 1:5) {
    norm = norm + nn.post(i, degree, m)
  }
  return(nn / norm)
}  
```

@@

```{r}
run.rsa <- function(d) {
  #BP------->
  #Get current matrix
  get.m = function(s, m) {
    m2 <- filter(m, scale == s) %>%
      spread(degree, speaker.p) %>%
      mutate(hi = hi / sum(hi), 
                  low = low / sum(low)) %>%
      select(hi, low)
    return(m2)
  }

  scale.matrix <- data %>% 
    select(stars, degree, speaker.p, prior.p) %>%
    mutate(listener.pred = norm.post(stars, degree, get.m(scale, .)))

  return scale.matrx$
 #BP------->

  #Old Mike code------>
  scale.matrix <- data %>% 
    select(stars, degree, speaker.p, prior.p) %>% 
    spread(degree, speaker.p) %>% 
    mutate(hi = hi / sum(hi), 
           low = low / sum(low)) %>%
    as.matrix

  preds <- expand.grid(stars = 1:5, 
              degree = c("low","hi")) %>%

    scale.matrix %>% 
    mutate(listener.pred = norm.post(stars, degree, get.m(scale, scale.matrix)))
  return(preds)
} 
```
